>

### 2020-09-24 manuscript/manuscript.Rmd
Clarify discussion of limitations, close #11

This paper applies a previously-presented but little-used accessibility
statistic that could, in theory, accommodate many attributes of the destination
parks as well as the people who might use them. As an illustration: the
park-going population could be separated into at least four delineated clusters,
each preferring different amenities of a park:
\begin{itemize}
 \item{runners and cyclists: long, interesting trail systems}
 \item{sports players: soccer fields, basketball courts, or baseball diamonds}
 \item{families with small children: water features and playgrounds}
 \item{casual users: water features, gardens, performances, etc.}
\end{itemize}
An analyst could then compute the utility-based accessibility for each cluster
with different utility values for each park's amenities, and obtain a measure of
a neighborhood's accessibility to park features that its residents most care
about. In this paper, we proceed only incrementally towards
this by adding some selected park amenities as an element of each park's
attractiveness above and beyond its size. The set of amenities we included in
the utility calculation --- and the contribution of each amenity to the overall
utility --- was dictated by the availability of data on the park amenities in New
York City and our ability to find comparable prior studies with transferrable
utility parameters. We can envision a study where mobile device data
revealing the home locations of park users would be paired with more detailed
park amenities and use data (e.g. geolocated Twitter data *a la*
@roberts2017using) to estimate the utility contribution of these features. This
could in turn provide a more nuanced understanding of the relationship between
park accessibility, use, and health outcomes.

>>>>

This paper applies a previously-presented but little-used accessibility
statistic that could, in theory, accommodate many attributes of the destination
parks as well as the people who might use them. As an illustration: the
park-going population could be separated into at least four delineated clusters,
each preferring different amenities of a park:
\begin{itemize}
 \item{runners and cyclists: long, interesting trail systems}
 \item{sports players: soccer fields, basketball courts, or baseball diamonds}
 \item{families with small children: water features and playgrounds}
 \item{casual users: water features, gardens, performances, etc.}
\end{itemize}
An analyst could then compute the utility-based accessibility for each cluster
with different utility values for each park's amenities, and obtain a measure of
a neighborhood's accessibility to park features that its residents most care
about. The set of amenities we included in
the utility calculation --- and the contribution of each amenity to the overall
utility --- was dictated by the availability of open data on the park amenities in New
York City and our ability to find comparable prior studies with transferable
utility parameters. It is remarkable that our two utility specifications --- one
with size and distance, and one with size and distance plus amenities --- result
in such similar model estimates. This may indicate that the utility is driven
largely by size and distance, or that the additional park amenities we included
in the utility specification are spatially distributed in a way that correlates
with the health outcomes. Either way, further analysis examining more amenity
variables is warranted.
 We can envision a study where mobile device data
revealing the home locations of park users would be paired with more detailed
park amenities and use data (e.g. geolocated Twitter data *a la*
@roberts2017using) to estimate the utility contribution of these features. This
could in turn provide a more nuanced understanding of the relationship between
park accessibility, use, and health outcomes.
